---
title: "Main"
author: "Arnav Bhutani"
date: "12/6/2020"
output: pdf_document
---
A non-commented version of this file is availabe [here](./main.R)

Initial Library Setup
```{r echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
devtools::load_all()
library(here)
library(readr)
library(tidyverse)
library(HMM)
library(Rcpp)
data = read_csv(here("/data/ex_data.csv"))
```


variable initialization. 
```{r}
hidden  = matrix(1/2, 2, 2)
visible = matrix(1:6, 2, 3)
visible = visible/rowSums(visible)
initial_distribution = c(1/2, 1/2)
```

Get the actual hidden and visible probabilities, as defined by the dataset.
```{r}
output = BaumWelch(data$Visible, hidden, visible, initial_distribution, n.iter = 100)
```


```{r}
output$switching
output$visible

write_rds(output, here("/data/hidden_visible.rds"))
```

Get the HMM library's output
```{r}
hmm = initHMM(c("A", "B"), c(1, 2, 3),
              startProbs = initial_distribution,
              transProbs = hidden,
              emissionProbs = visible)

hmm.out <- baumWelch(hmm, data$Visible, 100)

hmm.out$hmm$transProbs
hmm.out$hmm$emissionProbs

write_rds(hmm.out$hmm, here("/data/hmm_hidden_visible.rds"))
```

Create a 100 tests for each viterbi algorithm to find the most probable paths using the HMM package.
```{r}
test <- (map(seq(100, 10000, 100), ~ simHMM(hmm.out$hmm, .x)))

test[[1]]
```

Accuracy check for my model
```{r}
my_accuracy <- map(1:length(test), ~
                  sum(Viterbi(test[[.]]$observation,output$switching,output$visible,initial_distribution) != test[[.]]$states)/length(test[[.]]$states)
                )
my_accuracy[[1]]

write_rds(my_accuracy, here("/data/my_accuracy.rds"))
```

Similar accuracy check for HMM model
```{r}
hmm_accuracy <- map(1:length(test), ~
                      sum(viterbi(hmm, test[[.]]$observation) != test[[.]]$states)/length(test[[.]]$states))
hmm_accuracy[[1]]

write_rds(hmm_accuracy, here("/data/hmm_accuracy.rds"))
```


Create a plot of the two accuracies, and save it in the results folder.
```{r}
plot(seq(100, 10000, 100), my_accuracy, xlab = "HMM length", ylab = "accuracy", col = "red")
points(seq(100, 10000, 100), hmm_accuracy, col = "green")
dev.copy(png, here('/results/accuracy.png'))
dev.off()
```


Time the various functions:
```{r}
timings <- bench::mark(
  {
    Viterbi(data$Visible,output$switching,output$visible,initial_distribution)
  },
  {
    Viterbi_c(data$Visible,output$switching,output$visible,initial_distribution)
  },
  {
    viterbi(hmm.out$hmm, data$Visible)
  }
)

timings

write_rds(timings, here("/data/timings.rds"))
```


Name the timings and plot:
```{r}
timings$expression[1] <- "Viterbi (Bhutania)"
timings$expression[2] <- "Viterbi_c (Bhutania)"
timings$expression[3] <- "viterbi (HMM)"

plot(timings, type = "beeswarm")
dev.copy(png, here('/results/timing.png'))
dev.off()

```

